On Secure Delegation of SampBQP with a Classical Client

### 2020-01-01 hamiltonian.tex
Add discussion results

In this section, we give a reduction from $\SampBQP$ to a local Hamiltonian problem. \hannote{proofs in later sections?}

@@

\begin{theorem}
	Let $C$ be a circuit consisting of $T$ Hadamard or Toffoli gates. For any input string $x$,  there exists a local Hamiltonian $H_{C(x)}$  with the following properties:
	\begin{itemize}
		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$ with at most $O(T)$ terms
		\item $H_{C(x)}$ has a unique ground state  $\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t\ldots U_1\ket{x}\otimes\ket{\hat{t}}$ with eigenvalue $0$. We call the first register of $\ket{\psi_{C(x)}}$ the data register, and the second register of $\ket{\psi_{C(x)}}$ the time register.
		\item For any state $\ket\phi$ such that $\braket{\phi|\psi_{C(x)}}=0$,  $\braket{\phi|H_{C(x)}|\phi}>\frac{3}{4}$.
	\end{itemize}
\end{theorem}

\iffalse
\begin{definition}
	We call the first registers of $\ket{\psi_{C(x)}}$ the data register, and the later registers of $\psi_{C(x)}$ the time register.
\end{definition}
\fi

\begin{theorem}
	Given a circuit $C$ consisting of Hadamard and Toffoli gates, and an input string $x$, there ea $\BPP$ machine can construct a description of $H_{C(x)}$ in polynomial time.
\end{theorem}

\begin{theorem}
	Given circuit $C$ consisting of Hadamard and Toffoli gates, and $x\in\set{0,1}^*$, there exists an quantum algorithm that accepts $\ket{\psi_{C(x)}}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}$. Furthermore, this algorithm doesn't apply any quantum gates, and uses only $X$ and $Z$ measurements.
\end{theorem}

@@

\begin{observation}
	\label{idpadding}
	Given circuit $C$ and $x$, one can first pad $C$ with identity matrices at the end, doubling its number of gates and obtain $C'$. One can then measure the time register of $\ket{\psi_{C'(x)}}$ and obtain with probability $\frac{1}{2}$ the state $C(x)$.
\end{observation}

@@

Here we first prove that $\set{H, T}$ is a universal gate set. After this subsection, we'll be able to assume without loss of generality that all quantum circuits consists of only Toffoli and Hadamard gates. After doing that, we make a further observation that we'll use later.

We know that Hadamard gate and controlled phase gate is universal following \cite{quant-ph/0301040}:
$$H=\frac{1}{\sqrt{2}}\begin{pmatrix}1&1\\1&-1\end{pmatrix}$$
	$$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$
		Which is proven to be universal in \cite{kitaev_1997}.

Now we present a construction from \cite{quant-ph/0301040}.

\begin{theorem}
	Let $C$ be a circuit that:
	\begin{itemize}
		\item consists of $T$ gates, each either $H$ or $\Lambda(P(i))$.
		\item uses $n$ qubits
	\end{itemize}
	Then a classical machine given $C$ can compute a circuit $C'$ that:
	\begin{itemize}
		\item consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$.
		\item uses $n+1$ qubits
		\item Let $x\in\set{0,1}^n$. Let $x||0\in\set{0,1}^{n+1}$ be $x$ concatenated with $0$. The $X$ and $Z$ measurement results of $C(x)$ and the first $n$ qubits of $C'(x||0)$ are identically distributed.
	\end{itemize}
\end{theorem}

@@

	We construct $C'$ so that $\mathcal{F}\circ C=C'\circ\mathcal{F}$ by following the computation above. It satisfies the required properties by construction.
	\begin{itemize}
		\item $C'$ uses only Hadamard and Toffoli gates.
		\item Exchanging $\mathcal{F}$ with $H$ doesn't change the circuit size. Exchanging $\mathcal{F}$ with controlled phase gate turns it into $4$ gates. So the final result is at most $4T$ gates.
		\item When $x$ is classical, $\mathcal{F}(x)=x||0$. So $F\circ C(x)=C'(x||0)$. It is simple to verify that $F$ preserves $X$ and $Z$ measurement results on the first $n$ qubits.
	\end{itemize}
\end{proof}

@@

\subsection{Constructing a local Hamiltonian instance}

Here we reduce a circuit into a history XZ local Hamiltonian instance.

\begin{theorem}
	Let $C=U_T\ldots U_1$ be a circuit consisting of Hadamard and Toffoli gates, and let $x\in\set{0, 1}^*$. Then a classical machine can construct in polynomial time descriptions of some $H_{C(x)}\in\spn\mathcal{G}_{XZ}$ such that:
	\begin{itemize}
		\item its ground state is $$\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
		\item $\braket{\psi_{C(x)}|H_{C(x)}|\psi_{C(x)}}=0$
		\item $\forall\ket\phi,\braket{\phi|\psi_{C(x)}}=0\Rightarrow\braket{\phi|H_{C(x)}|\phi}\geq\frac{3}{4}$
		\item Has $O(T)$ nonzero components whose coefficients are each at most $O(T^3)$.
	\end{itemize}
\end{theorem}

\begin{proof}
	We ensure states perpendicular to $\ket{\psi_{C(x)}}$ have high eigenvalues. The base construction comes from \cite{kitaev2002classical}. The simplification to $\spn\mathcal{G}_{XZ}$ is taken from \cite{PhysRevA.78.012352}.

@@

	\begin{lemma}
		$$K_{clock}\cap K_{prop}=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}: \ket{y}\in\mathcal{B}^{\otimes n}}$$
	\end{lemma}

@@

\subsection{Checking for ground state}

Now we put the above results in term of measurement outputs.

\begin{algorithm}
	\caption{Check for ground state}
	\label{AlgGroundStateCheck}
	\begin{algorithmic}[1]
		\Require $H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$
		\Procedure{GroundStateCheck}{$\ket\phi$}
		\State $D\gets\sum_{S\in\mathcal{G}_{XZ}}|d_S|$
		\State $p_S\gets\frac{|d_S|}{D}$
		\State $\widetilde{S}\gets$ Pick weighted using $p_S$
		\State $\lambda_{\widetilde{S}}\gets$ Measure $\ket\phi$ in the $\widetilde{S}$ basis
		\If{$\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$}
		\State Accept
		\Else
		\State Reject
		\EndIf
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

>>>>

In this section, we give a reduction from $\SampBQP$ to a local Hamiltonian problem. \hannote{put proofs back. Adiabatic ref?}

\Ethan{Adiabatic and spectral gap ref = \cite{adiabatic}}

@@

\begin{theorem}
	Let $C$ be a circuit consisting of $T$ Hadamard or Toffoli gates. For any input string $x$,  there exists a local Hamiltonian $H_{C(x)}$  with the following properties:
	\begin{itemize}
		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$ with at most $O(T)$ terms
		\item $H_{C(x)}$ has a unique ground state  $\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t\ldots U_1\ket{x}\otimes\ket{\hat{t}}$ with eigenvalue $0$. We call the first register of $\ket{\psi_{C(x)}}$ the data register, and the second register of $\ket{\psi_{C(x)}}$ the time register.
		\item For any state $\ket\phi$ such that $\braket{\phi|\psi_{C(x)}}=0$,  $\braket{\phi|H_{C(x)}|\phi}>\frac{3}{4}$.
	\end{itemize}

	Furthermore, there exists a $\BPP$ machine that can construct a description of $H_{C(x)}$ in polynomial time.
\end{theorem}

\iffalse
\begin{definition}
	We call the first registers of $\ket{\psi_{C(x)}}$ the data register, and the later registers of $\psi_{C(x)}$ the time register.
\end{definition}

\begin{theorem}
	Given a circuit $C$ consisting of Hadamard and Toffoli gates and an input string $x$, there exists a $\BPP$ machine that can construct a description of $H_{C(x)}$ in polynomial time.
\end{theorem}
\fi

\begin{theorem}
	Given circuit $C$ consisting of Hadamard and Toffoli gates and an input string $x\in\set{0,1}^*$, there exists an quantum algorithm that accepts $\ket{\phi}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H_{C(x)}|\phi}$. In particular, it accepts the $\ket{psi_{C(x)}}$ with probability $\fot$. Furthermore, this algorithm doesn't apply any quantum gates, using only $X$ and $Z$ measurements.
\end{theorem}

@@

\begin{observation}
	\label{idpadding}
	Given a circuit $C$ and an input string $x$, one can first pad $C$ with identity matrices at the end, doubling its number of gates and obtaining another circuit $C'$. One can then measure the time register of $\ket{\psi_{C'(x)}}$ and obtain with probability $\frac{1}{2}$ the state $C(x)$.
\end{observation}

@@

\hannote{throw this into appendix?}
 Here we restate the result from from \cite{quant-ph/0301040} showing that $\set{H, \Lambda^2(X)}$ is a universal gate set. Because of this result, we cam assume without loss of generality that all quantum circuits consists of only Toffoli and Hadamard gates.

 %After this subsection, we'll be able to assume without loss of generality that all quantum circuits consists of only Toffoli and Hadamard gates. %After doing that, we make a further observation that we'll use later.

\hannote{theorem?} We know that Hadamard gate and controlled phase gate is universal from \cite{kitaev_1997}
$$H=\frac{1}{\sqrt{2}}\begin{pmatrix}1&1\\1&-1\end{pmatrix}$$
	$$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$

Now we present the construction from \cite{quant-ph/0301040}.

\begin{theorem}
	Let $C$ be a circuit that:
	\begin{itemize}
		\item consists of either $H$ or $\Lambda(P(i))$, and the number of gates is $T$.\hannote{confusing?}
		\item uses $n$ qubits
	\end{itemize}
	Then a classical machine given $C$ can compute a circuit $C'$ that:
	\begin{itemize}
		\item consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$ \hannote{don't like this notation}.
		\item uses $n+1$ qubits
		\item Let $x\in\set{0,1}^n$. Let $x|| 0\in\set{0,1}^{n+1}$ be $x$ concatenated with $0$.
		The measurement result of a tensor product of $X$ and $Z$ operators on the first $n$ qubits of $C'(x||0)$ has the same distribution as that on $C(x)$.
		%The $X$ and $Z$ measurement results of $C(x)$ and the first $n$ qubits of $C'(x||0)$ are identically distributed.
	\end{itemize}
\end{theorem}

@@

	We construct $C'$ so that $\mathcal{F}\circ C=C'\circ\mathcal{F}$ by following the computation above. It satisfies the required properties by construction.
	\begin{itemize}
		\item $C'$ uses only Hadamard and Toffoli gates.
		\item Exchanging $\mathcal{F}$ with $H$ doesn't change the circuit size. Exchanging $\mathcal{F}$ with controlled phase gate turns it into $4$ gates. So the final result is at most $4T$ gates.
		\item When $x$ is classical, $\mathcal{F}(x)=x||0$. So $F\circ C(x)=C'(x||0)$. It is simple \hannote{need a little more work?}to verify that $\mathcal{F}$ preserves $X$ and $Z$ measurement results on the first $n$ qubits.
	\end{itemize}
\end{proof}

@@

\subsection{Reducing $\SampBQP$ to  local Hamiltonian }

In this section, we show how to reduce a $\SampBQP$ circuit to a  local-$XZ$-Hamiltonian.

\begin{theorem}
	Let $C=U_T\ldots U_1$ be a circuit consisting of Hadamard and Toffoli gates, and let $x\in\set{0, 1}^n$. Then there exists a $\BPP$  machine which generates the  description of a $H_{C(x)}\in\spn\mathcal{G}_{XZ}$ such that:
	\begin{itemize}
		\item its unique ground state is $$\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
		\item $\braket{\psi_{C(x)}|H_{C(x)}|\psi_{C(x)}}=0$
		\item $\forall\ket\phi,\braket{\phi|\psi_{C(x)}}=0\Rightarrow\braket{\phi|H_{C(x)}|\phi}\geq\frac{3}{4}$
		\item $H_{C(x)}$ has $O(T)$ nonzero terms whose coefficients are  at most $O(T^3)$.
	\end{itemize}
\end{theorem}

\begin{proof}
	We need to ensure the excited states of $H_{C(x)}$ have high eigenvalues. The base construction comes from \cite{kitaev2002classical}. The simplification to $\spn\mathcal{G}_{XZ}$ is taken from \cite{PhysRevA.78.012352}.

@@

	\begin{lemma} \hannote{throw outside? or just merge}
		$$K_{clock}\cap K_{prop}=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}: \ket{y}\in\mathcal{B}^{\otimes n}}$$
	\end{lemma}

@@

\subsection{Checking the ground state of the local Hamiltonian}

%Now we put the above results in term of measurement outputs.\hannote{???}

We present an algorithm that checks whether a given state is the ground state of some fixed $H_{C(x)}$ following~\cite{PhysRevA.93.022326}.

\begin{algorithm}
	\caption{Check for ground state}
	\label{AlgGroundStateCheck}
	\begin{algorithmic}[1]
		\Require $H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$
		\Procedure{GroundStateCheck}{$\ket\phi$}
		\State Set $D = \sum_{S\in\mathcal{G}_{XZ}}|d_S|$
		\State Set $p_S = \frac{|d_S|}{D}$
		\State Sample $\widetilde{S}$ from $\mathcal{G}_{XZ}$, weighted by $p_S$.
		\State  Measure $\ket\phi$ in the $\widetilde{S}$ basis, recording the result as $\lambda_{\widetilde{S}}$.
		\If{$\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$}
		\State Accept
		\Else
		\State Reject
		\EndIf
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

### 2020-01-01 preliminaries.tex
Add discussion results

@@

We  classify the interaction between a (almost classical) client and a quantum server for sampling problems, extending the classification by \cite{mahadev_delegation}.

>>>>

\begin{rmk}
\hannote{sampling generalize decision blah}
\end{rmk}

@@

\subsection{Quantum Prover Interactive Protocol (QPIP)}
We  classify the interaction between a (almost classical) client and a quantum server for sampling problems, extending the classification by \cite{mahadev_delegation}.

### 2020-01-01 qpip.tex
Add discussion results

Here we create a $\QPIP_1$ scheme for $\SampBQP$ by constructing a history XZ local Hamiltonian instance, and ask the prover to provide the ground state. In the case for decision problems, it would be a simple Chernoff bound as in \cite{kitaev2002classical}. A prover, honest or not, couldn't do better than sending $n$ identical copies of some state. The same reasoning does not generalize to our case, so instead we give the following construction.

We then extend our scheme for $\QPIP_0$, by using results from \cite{mahadev_delegation}.

@@

\begin{observation}
	\label{ProtoGroundStateCheck}
	There is a $\QPIP_1$ protocol for \autoref{AlgGroundStateCheck}. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
\end{observation}
\begin{proof}
	The prover simply sends the input qubit-by-qubit for the verifier to measure. It is clear that any attacks on this scheme trivially maps onto an attack on the original scheme.
\end{proof}

\begin{theorem}
	Let $L\in\SampBQP$. Then there exists some $\QPIP_1$ protocol for $L$ with completeness negligible to perfect and soundness $(O(T^{-c}), O(T^{-c}))$ for any constant $c$. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
\end{theorem}
\begin{proof}
	Set the following variables
	\begin{itemize}
		\item $\varepsilon=T^{-c}$
		\item $m$ large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
		\item $n$ large enough so the following quantities are negligible in $\varepsilon$ by the Chernoff bound:
			\begin{itemize}
				\item[$\circ$] $P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$
				\item[$\circ$] $P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$
			\end{itemize}
		\item $N$ large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.
	\end{itemize}

	With these parameters, we claim that \hyperref[ProtoQPIP1]{Protocol~\ref*{ProtoQPIP1}} does what is required.
	\floatname{algorithm}{Protocol}
	\begin{algorithm}
		\caption{Our $\QPIP_1$ protocol}
		\label{ProtoQPIP1}
		\begin{algorithmic}[1]
			\State The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
			\State The verifier randomly picks $m$ copies for outputting and $n$ copies for checking
			\State $c\gets0$
			\State $y\gets\bot$
			\For{$i\gets1, N$}
			    \If{Copy is for checking}
				\State The verifier runs \autoref{AlgGroundStateCheck} as described by \hyperref[ProtoGroundStateCheck]{Observation~\ref*{ProtoGroundStateCheck}}.
			    \If{Test passes}
			        $c\gets c+1$
			    \EndIf
			    \ElsIf{Copy is for outputting}
			    \State The verifier measures the copy in standard basis
			    \If{measurement result of the clock register $\geq\frac{T}{2}$}
			        \If{$y=\bot$}
			            \State $y\gets$ measurement result of the data register
                    \EndIf
			    \EndIf
			    \Else
			    \State The verifier measures the entire register in standard basis
			    \EndIf
			\EndFor
			\If{$\frac{c}{n}\geq\frac{1}{2}-\varepsilon$}
			\If{$y\ne\bot$}
			\State output $y$
			\Else
			\State Reject
			\EndIf
			\Else
			\State Reject
			\EndIf
		\end{algorithmic}
	\end{algorithm}

@@

Here we combine the above scheme with results from \cite{mahadev_delegation} to create a delegation protocol for $\SampBQP$ for fully classical clients.

We first describe the construction in \cite{mahadev_delegation}.

\begin{theorem}
	Under the assumption that the learning with errors problem with superpolynomial noise ratio is computationally intractable for an efficient quantum machine, there exists a $\QPIP_0$ protocol that...
	\begin{itemize}
		\item x
		\item y
		\item z
	\end{itemize}
\end{theorem}
\begin{proof}
	Construction given in \cite{mahadev_delegation}
\end{proof}

\Ethan{TODO}

>>>>

Here we create a $\QPIP_1$ scheme for $\SampBQP$ by constructing a history XZ local Hamiltonian instance, and ask the prover to provide the ground state. In the case of decision problems, it would be a simple Chernoff bound as in \cite{kitaev2002classical}. A prover, honest or not, couldn't do better than sending $n$ identical copies of some state. The same reasoning does not work in  our case, so  we give the following construction instead.

We then extend our scheme for $\QPIP_0$ using results from \cite{mahadev_delegation}.

@@

\begin{observation}
	\label{ProtoGroundStateCheck}
	There is a $\QPIP_1$ protocol for \autoref{AlgGroundStateCheck}. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
\end{observation}
\begin{proof}
	The prover simply sends the input qubit-by-qubit for the verifier to measure. It is clear that any attacks on this scheme trivially maps onto an attack on the original scheme.
\end{proof}
\hannote{something. pull protocol out?}
\begin{theorem}
    \label{QPIP1thm}
	For any $L\in\SampBQP$,  there exists a $\QPIP_1$ protocol for $L$ with negligible completeness and soundness $(O(T^{-c}), O(T^{-c}))$ for any constant $c$. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
\end{theorem}
\begin{proof}
	Set the following variables
	\begin{itemize}
		\item $\varepsilon=T^{-c}$
		\item $m$ large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
		\item $n$ large enough so the following quantities are negligible in $\varepsilon$ by the Chernoff bound:
			\begin{itemize}
				\item[$\circ$] $P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$
				\item[$\circ$] $P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$
			\end{itemize}
		\item $N$ large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.
	\end{itemize}

	With these parameters, we claim that \hyperref[ProtoQPIP1]{Protocol~\ref*{ProtoQPIP1}} does what is required.
	\floatname{algorithm}{Protocol}
	\begin{algorithm}
		\caption{ $\QPIP_1$ protocol for $\SampBQP$}
		\label{ProtoQPIP1}
		\begin{algorithmic}[1]
			\State The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
			\State The verifier randomly picks $m$ copies for outputting and $n$ copies for checking
			\State $c\gets0$
			\State $y\gets\bot$
			\For{$i\gets1, N$}
			    \If{Copy is for checking}
				\State The verifier runs \autoref{AlgGroundStateCheck} as described by \hyperref[ProtoGroundStateCheck]{Observation~\ref*{ProtoGroundStateCheck}}.
			    \If{Test passes}
			        $c\gets c+1$
			    \EndIf
			    \ElsIf{Copy is for outputting}
			    \State The verifier measures the copy in standard basis
			    \If{measurement result of the clock register $\geq\frac{T}{2}$}
			        \If{$y=\bot$}
			            \State $y\gets$ measurement result of the data register
                    \EndIf
			    \EndIf
			    \Else
			    \State The verifier measures the entire register in standard basis
			    \EndIf
			\EndFor
			\If{$\frac{c}{n}\geq\frac{1}{2}-\varepsilon$}
			\If{$y\ne\bot$}
			\State output $y$
			\Else
			\State Reject
			\EndIf
			\Else
			\State Reject
			\EndIf
		\end{algorithmic}
	\end{algorithm}

@@

Here we combine \autoref{QPIP1thm} with results from \cite{mahadev_delegation} to create a delegation protocol for $\SampBQP$ for fully classical clients.

We first restate the construction in \cite{mahadev_delegation}.

Let $\rho$ be an $n$-qubit state. Let $h$ be an n-bits string called the \emph{basis choice}. That is, $h_i=0$ indicates that the $i$-th qubit of $\rho$ is to be measured in the standard basis, while $i=1$ indicates Hadamard basis measurement instead. Let $D_{\rho, h}$ be the distribution of the corresponding measurement results.

\begin{theorem}
    \label{Mahadev_QPIP0_Protocol_Interface}
	Under the assumption that the learning with errors problem with superpolynomial noise ratio is computationally intractable for an efficient quantum machine, there exists a $\QPIP_0$ protocol $(\bbV, \bbP)$ with the following properties:
	\begin{itemize}
	    \item The protocol runs either a ``Hadamard round" or a ``test round" with probability $\fot$ each.
	    \item With a test round, the verifier outputs nothing other than accept/reject
	    \item With a Hadamard round, for prover $\bbP'$, the verifier also obtains a sample from $D_{\bbP', h}$. We define $D^C_{\bbP', h}$ as that distribution conditioned on acceptance.
	    \item (completeness) $\forall n\in\mathcal{B}^{\otimes n}, h\in\bbN$ and $h$, there is a prover with negligible reject probability. Furthermore, $D^C_{\bbP, h}$ has negligible total variation distance to $D_\rho, h$
	    \item (soundness) Fix $\bbP'$ and $h$. Let $p_{h, H}$ be its rejection probability under a Hadamard round, and $p_{h, T}$ be its rejection probability under a test round. Then $\exists\tilde\bbP$ s.t. $\norm{D^C_{\bbP', h} - D_{\tilde\bbP, h}}\leq p_{h,H} + \sqrt{p_{h, T}}+\mu$ for some negligible $\mu$, and $\exists\rho$ s.t. $D_{\tilde\bbP, h}$ is computationally indistinguishable from $D_{\rho, h}$.
	\end{itemize}
\end{theorem}

\Ethan{Maybe wrap the below into a protocol?}

Let $\varepsilon>0$. Pick $N$ large enough so that by geometric probability getting a 
We pick $h$ the same way as we'd decide the measurement basis as in \Ethan{TODO ref protocol 2}.

\Ethan{TODO analyze that the above actually works?}
